Creating More Meaningful Explanations for Audio Deepfake Detection

### 2025-02-13 draft.tex
improvements to the equations of importance and trust
improve the description of the perceptible features, including the reason for choice

			The features we consider imperceptible are described as follows:
					Mel-spectrograms: A widely-used imperceptible feature in synthetic audio
					detection, the mel-spectrogram is a spectrographic representation of an audio
					sample transformed in a manner to better represent human perception of
					frequencies \cite{qais_deepfake_2022}.
					Mel-frequency cepstral coefficients: The derivative cepstral coefficients of
					the mel-spectrogram also considered imperceptible, also widely-seen in
					research on synthetic audio detection.

@@

			\[\frac{\sum_{s \in S} |w_{fs}|}{|S|}\]

@@

			\[\frac{\sum_{s \in S} w_{fs}(2l_{s}-1)}{|S|}\]

>>>>

			We also chose to include two perceptible features in our hybrid model, due to the
			performance-enhancing impact that perceptible features can have
			\cite{chaiwongyen_deepfake-speech_2023} when paired with perceptible features. These
			features are the mel-spectrogram and their derivative mel-frequency cepstral
			coefficients. We choose these features because they are well established in the
			research and have demonstrated consistent good performance in other examples,
			\cite{qais_deepfake_2022,anagha_audio_2023,fathan_mel-spectrogram_2022,
			altalahin_unmasking_2023,hamza_deepfake_2022,yan_initial_2022}. They allow for a
			spectrographic representation and analysis of an audio sample transformed in a way to
			better represent human perception of frequencies \cite{qais_deepfake_2022}.

@@

			\[I(f) = \frac{\sum_{s \in S} |w_{fs}|}{|S|}.\]

@@

			\[T(f) = \frac{\sum_{s \in S} w_{fs}(2l_{s}-1)}{|S|}.\]
